Title field: summary

### 2021-01-29 inst/examples/title.Rmd
added uniquetitles.png

---
title: "Title field: summary"
author: "Leo Lahti"
date: "`r Sys.Date()`"
output: markdown_document
---

@@

>>>>

---
title: "Title field: summary"
author: "Leo Lahti"
date: "`r Sys.Date()`"
output: md_document
---

@@

```{r uniquetitles, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8, fig.height=6}
library(ggplot2)
p <- ggplot(df.tmp, aes(freq, color = "black"))+ geom_bar(width=0.05, colour="blue")+scale_x_log10()+ scale_y_log10()
print(p) 
```
